\huge A Usability Evaluation of Tor Launcher

### 2016-11-17 pets2017-paper/pets2017-paper.tex
update with accurate demographics

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface. Of the 114, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit one participant's information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface. Of the 114, one participant did not report their demographics. We still use their experiment data. Of the 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
